Non-kissing and non-crossing complexes \\ for gentle algebras

### 2018-07-02 draft/accordionComplexSurfaces.tex
definition slalom

\begin{definition}
\label{def:slalom}
A \defn{$\dissection\dual$-slalom} is a $B$-arc~$\alpha$ of~$\bar\surface$ such that, whenever~$\alpha$ crosses an edge~$a$ of~$\dissection$ contained in two faces~$f,g$ of~$\dissection$, the marked points~$f\dual$ and~$g\dual$ lie on opposite sides of~$\alpha$ in the union of~$f$ and~$g$ glued along~$a$.
\end{definition}

>>>>

\begin{definition}
\label{def:slalom}
A \defn{$\dissection\dual$-slalom} is a $B$-curve~$\alpha$ of~$\bar\surface$ such that, whenever~$\alpha$ crosses an edge~$a$ of~$\dissection$ contained in two faces~$f,g$ of~$\dissection$, the marked points~$f\dual$ and~$g\dual$ lie on opposite sides of~$\alpha$ in the union of~$f$ and~$g$ glued along~$a$.
Here, we consider that~$f\dual$ lies on the right (resp.~left) of~$\alpha$ when~$\alpha$ circles clockwise (resp.~counterclockwise) around~$f\dual$.
\end{definition}
